---
title: "energy_data"
author: "FZ"
date: "4/9/2021"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}

library(tidyverse)
library(lubridate)

```

## Data

Data is collected very irregularly over time. Only useful at day-scale.
Some houses have less data than others (|house1| > |house4|).

```{r}

house <- read_csv("data/house1.csv") %>%
  rename(date = "X1") %>%
  mutate(date = ymd_hms(date), 
         h = hour(date), m = minute(date), s = second(date)) %>%
  unite("time", c("h", "m", "s"), sep = ":")

house %>% names()

house %>% head()

```

## Data contains:

- 12 days of data in month 4 and 11 in month 5 in 2011. 
- Data is collected every second all day long.

```{r}

house %>%
  distinct(year(date), month = month(date), day = day(date)) %>%
  mutate(n = 1) %>%
  group_by(month) %>%
  summarise(sum(n))


house %>%
  distinct(second = second(date)) %>%
  arrange(second)

house %>%
  distinct(hour = hour(date)) %>%
  arrange(hour)

house %>%
  dim()

```

- 23 consecutive days since April to May 27.

```{r}

house %>%
  distinct(d = day(date), m = month(date)) %>%
  arrange(m, d)

```

## All appliances:

```{r}

house %>%
  pivot_longer(cols = -c(date, time), 
               names_to = "appliance", values_to = "consumption") %>%
  ggplot(aes(date, consumption, color = appliance)) +
  geom_line() +
  facet_wrap(~appliance, scales = "free_y") +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

- Daily consumption changes over time: no consumption around may 16.

```{r}

house %>%
  filter(day(date) == 20) %>%
  pivot_longer(cols = -c(date, time), 
               names_to = "appliance", values_to = "consumption") %>%
  ggplot(aes(date, consumption)) +
  geom_line() +
  facet_wrap(~appliance, scales = "free_y") +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "A Day of consumption")

```

```{r}

mean_hour_c <-
  house %>%
    pivot_longer(cols = -c(date, time), 
                 names_to = "appliance", values_to = "consumption") %>%
    mutate(h = hour(date)) %>%
    group_by(appliance, h) %>%
    summarise(m_consumption = mean(consumption), 
              sd_consumption = sd(consumption)) 

```

### High variance but same pattern:

```{r}

mean_hour_c %>%
  ggplot() +
  geom_line(aes(h, m_consumption)) +
  facet_wrap(~appliance, scales = "free_y") +
  theme(legend.position = "none")

mean_hour_c %>%
  ggplot() +
  geom_line(aes(h, m_consumption)) +
  geom_line(aes(h, m_consumption + sd_consumption), color = "red") +
  facet_wrap(~appliance, scales = "free_y") +
  theme(legend.position = "none")

```
### What do different households have in common?


```{r}

house_files = list.files(path = "./data/", pattern = ".csv")
n_houses <- length(house_files)
house_dfs <- lapply(paste("./data/", house_files, sep = ""), read_csv)


process_data <- function(df, house_number) {
  
    df <-
      df %>%
      rename(date = "X1") %>%
      mutate(house = house_number, 
             date = ymd_hms(date), 
             h = hour(date), m = minute(date), s = second(date)) %>%
      unite("time", c("h", "m", "s"), sep = ":") %>%
      pivot_longer(cols = -c(date, time, house), 
                   names_to = "appliance", values_to = "consumption") %>%
      mutate(h = hour(date)) %>%
      group_by(house, appliance, h) %>%
      summarise(m_consumption = mean(consumption), 
                sd_consumption = sd(consumption)) 
    
    return(df)
}

house1_msd <- process_data(house_dfs[[1]], 1)
house2_msd <- process_data(house_dfs[[2]], 2)
house3_msd <- process_data(house_dfs[[3]], 3)
house4_msd <- process_data(house_dfs[[4]], 4)
house5_msd <- process_data(house_dfs[[5]], 5)
house6_msd <- process_data(house_dfs[[6]], 6)

houses <- bind_rows(house1_msd, house2_msd, house3_msd,
                    house4_msd, house5_msd, house6_msd)

houses %>% 
  distinct(appliance) %>%
  .$appliance

```
```{r}



```
